\mytitle

### 2022-01-01 paper.tex
typo

In this paper different approaches for the numerical calculation of
the real dilogarithm have been compared w.r.t.\ their potential for
the use of instruction\-/level (ILP) parallelism.  We found that a
rational minimax approximant in combination with Estrin's scheme to
evaluate the numerator/denominator polynomials provides both a
sufficient numerical precision and a high degree of ILP, potentially
leading to a reduced run\-/time when executed on a appropriate CPUs.
A corresponding approximant and a C implementation have been proposed
and compared to several existing implementations w.r.t.\ their
run\-/time.  The C implementation of the presented approximant can be
found in the appendix.  C++, Fortran, Julia and Rust implementations
can be found in \cite{polylogarithm,PolyLog.jl,polylog}, respectively.

>>>>

In this paper different approaches for the numerical calculation of
the real dilogarithm have been compared w.r.t.\ their potential for
the use of instruction\-/level parallelism (ILP).  We found that a
rational minimax approximant in combination with Estrin's scheme to
evaluate the numerator/denominator polynomials provides both a
sufficient numerical precision and a high degree of ILP, potentially
leading to a reduced run\-/time when executed on a appropriate CPUs.
A corresponding approximant and a C implementation have been proposed
and compared to several existing implementations w.r.t.\ their
run\-/time.  The C implementation of the presented approximant can be
found in the appendix.  C++, Fortran, Julia and Rust implementations
can be found in \cite{polylogarithm,PolyLog.jl,polylog}, respectively.
